% Discussion
% Three subsections: failure analysis, key insights and practical implications,
% future work.

\section{Discussion}
\label{sec:discussion}

\subsection{Failure Analysis}
\label{sec:disc-failures}

In this section we conduct a manual qualitative analysis to better understand the misclassification patterns across the explored IRC methods. We inspect the misclassifications produced by Qwen-32B (the strongest model) under each method's best configuration. From all the misclassifications across \ragtag. \bragtag, and fine-tune, we drew a random sample of 50 misclassifications per method (150 total). Each Method's sample includes 30 true-question, 10 true-bug, and 10 true-feature errors. Each case was analyzed by two authors independently, with discrepancies resolved through discussions. The identified failure categories and their frequencies are as follows:

\textbf{\textit{Wrong template format (77.33\%).}} Issue reports whose content and ground-truth label contradicts their chosen template and structure. All of these errors are from questions and feature requests that the user filed under a bug-report template (\textit{Steps to reproduce}, \textit{Expected}, \textit{Actual}, \textit{System Information}). Consequently, the structure of the bug template misleads the LLM classifier towards predicting bug, regardless of the issue's content. For example, \texttt{microsoft/vscode\#193985}\footnote{\url{https://github.com/microsoft/vscode/issues/193985}} is an actual support question that opens with a literal \texttt{Type: Bug} because it uses VS Code's bug template.

\textbf{\textit{Hybrid intent (13.33\%).}} Issues that could have multiple defensible labels due to their combined intents. These errors mostly take place when a fix or a feature request is layered in a question or bug. For example, in \texttt{kubernetes/kubernetes\#120364}\footnote{\url{https://github.com/kubernetes/kubernetes/issues/120364}} the author both reports a concrete bug and in the same body explicitly requests a new feature: ``\textit{Please, give us multiarchitecture image! and fix monoarchitecture images too!}''

\textbf{\textit{Label noise (9.33\%).}} Issues whose ground-truth label does not match its content. For example, \texttt{tensorflow/tensorflow\#61710}\footnote{\url{https://github.com/tensorflow/tensorflow/issues/61710}} is titled ``\textit{Will there a MLP model in the future version?}'' which requests a new API feature for building MLPs. Yet the dataset labels it as a bug.


We also sampled 30 issues with \textit{invalid} predictions per method (60 total) and observed two failure modes. In roughly 74\% of cases, the model kept generating prose past the label slot --- either continuing the issue-body content (extra \textit{Steps to reproduce} fields, stack traces, code) or its own chain-of-thought reasoning --- without ever emitting a structured label. The remaining 26\% are degenerate hallucinations: repeated digits, repeated punctuation, or out-of-schema labels (e.g., \texttt{docs}) that cannot be parsed into any of the three classes.



\subsection{Key Insights and Practical Implications}
\label{sec:disc-insights}

The experiments and the failure analysis in \Cref{sec:disc-failures} together yield several actionable insights for practitioners deploying IRC and for researchers building on this benchmark.

\textbf{The bug bias is structural, not parametric.} The misclassification asymmetry of question issues toward bug appears in every method we evaluated. \votag, which has no LLM, predicts bug for 32\% of true-question issues at its best $k$ (\Cref{sec:rq1}). Zero-shot \ragtag, which has no retrieval, predicts bug for 46--59\% of true-question issues across the four model sizes (\Cref{sec:ragtag}). Fine-tuning on the same train split inherits the skew as well, with question consistently the lowest-$F_1$ class across all three approaches (\Cref{tab:method-comparison}). The bias survives both the removal of the LLM and the removal of retrieval, and prior work reports the same dominant error pattern on different LLMs and datasets~\cite{colavito2025benchmarking,colavito2024impact} --- which suggests that the asymmetry is a property of the IRC task and the embedding space rather than of any specific model family. A direct measurement on our data supports this reading: for true-question queries, the average label imbalance among the top-$k$ neighbors is $N_\text{bug} - N_\text{question} = -1.4$ averaged across $k\in[1,30]$, while bug queries retrieve overwhelmingly bug neighbors. \bragtag\ targets the retrieval side of this mechanism by removing bug examples from the prompt only when the query's neighborhood is roughly balanced between bug and question, and the failure analysis confirms the intervention reaches its target population: the retrieval-skew rate drops from 26\% (\ragtag) to 14\% (\bragtag), exactly halving the share of misclassifications driven by a wrong-class-dominated neighborhood.

\textbf{Statistical equivalence at the dataset-noise ceiling.} The aggregate (\bragtag\ $-$ fine-tune) macro $F_1$ difference is $+0.001$ with paired bootstrap 95\% CI $[-0.007, +0.008]$, passing TOST equivalence at $\delta{=}0.01$ (\Cref{sec:method-comparison}), despite \bragtag\ retrieving from only 300 labeled issues per project while fine-tune trains on 3{,}300. The failure analysis recasts this equivalence: only 3\% of residual misclassifications are clean errors with no template confound and no plausible label ambiguity (\Cref{sec:disc-failures}). The other 97\% involve either a wrong-template confound (76\%, where the bug-report scaffolding pushes the classifier away from the user's true intent), label noise (9\%), or genuinely ambiguous hybrid intents (13\%). Both methods do not match because they are independently equally accurate; both reach a regime where the residual error is dominated by inputs whose templates or labels make the classification ambiguous within the three-class schema. The practical implication is that further gains on this benchmark are unlikely to come from stronger LLMs alone --- they will require either label cleaning, template-aware preprocessing, or a richer label space.

\textbf{Match the method to the labeled-data scope.} \ragtag\ and fine-tuning respond to the PS--PA distinction in opposite directions. \ragtag's best setting is PS at every (model, $k{\geq}1$) pair (\Cref{sec:ragtag}); fine-tune's best setting is PA at every model size, by $+0.031$ to $+0.084$ macro $F_1$ (\Cref{sec:finetune-eval}). The structural reason is that PS retrieval indexes 300 issues from the same project as the query, and same-project issues cluster together in the embedding space, so the small index covers most of the relevant neighborhood; we measured PA and PS to share 84--90\% of the top-$k$ neighbors across $k\in[3,30]$ in \Cref{sec:rq1}. PS is therefore not just a smaller retrieval pool but a near-complete one for a retrieval-based method. Fine-tuning has no such property: 300 labeled issues per project are insufficient to fit the question/bug/feature distinction, and the model benefits from the broader 3{,}300-issue PA pool. The practical recommendation is therefore conditional on what labeled data a project has available: with $\sim$300 in-project labeled issues, retrieval-augmented few-shot is the stronger choice, while $\sim$3{,}300 issues spanning multiple projects make fine-tuning competitive. \bragtag\ extends the first regime: at 300 in-project labels, it matches fine-tune's 3{,}300-issue PA performance to within statistical equivalence. The 11$\times$ data factor between settings is the operationally important takeaway for projects without a cross-project label corpus.

\textbf{Cost crossover at large model size.} Wall-time and memory characteristics differ qualitatively across methods. Fine-tune carries a fixed training cost that grows roughly linearly with model size, while \ragtag\ and \bragtag\ have no training phase but scale inference time with prompt length. The ordering inverts at the largest model size: at Qwen-32B, fine-tune's total wall-time (2.71 h) is shorter than both \ragtag\ (4.62 h) and \bragtag\ (4.15 h), even though fine-tune is more expensive at every smaller size. The crossover is driven by long-context inference cost overtaking training cost as model size grows but the best $k$ stays fixed at 12 (\Cref{sec:method-comparison}). The retrieval-based methods are therefore most cost-favorable in the model-size range a single consumer GPU can host (3B, 7B, 14B); at 32B and beyond, fine-tuning may be the more efficient workflow if the labeled-data conditions favor it.

\textbf{Class balance is a hidden axis of comparison.} \bragtag\ is the most class-balanced of the three methods. Averaged across the four model sizes, the per-class $F_1$ standard deviation is 0.053 for \bragtag, 0.066 for fine-tune, and 0.076 for \ragtag, and the worst-class $F_1$ floor is 0.694, 0.672, and 0.638 respectively (\Cref{tab:method-comparison}). Aggregate macro $F_1$ does not capture this: a method that is uniformly competent across the three labels can be preferable for triage deployment to one with the same macro $F_1$ but a noticeable per-class trough. \bragtag's intervention specifically lifts the question floor without sacrificing the other two classes, making it the most stable choice when no single label can be allowed to degrade.

\textbf{Fine-tuning memorizes template surface signals.} A finding that emerges only from the qualitative analysis is that fine-tune's residual errors include a notable concentration on a single tooling-driven template artifact: issues filed via VS Code's ``\textit{Help $\to$ Report Issue}'' menu, which embeds a literal ``\textit{Type: Bug}'' marker regardless of intent (\Cref{sec:disc-failures}). Fine-tuning learned this surface signal as bug-predictive and over-applies it. Retrieval-based methods, which never see all 3{,}300 issues at once, are less prone to memorizing such template artifacts. This is a concrete, dataset-grounded reason to prefer in-context methods when a project's issue tracker contains tooling-driven template noise.


\subsection{Future Work}
\label{sec:disc-future}

\textbf{Tighter debiasing interventions.} \bragtag's margin-based filter halves the retrieval-skew rate (26\%$\rightarrow$14\%) but does not eliminate it. The remaining 14\% of misclassifications still occur on queries whose top-$k$ neighborhood is dominated by the wrong class even after bug examples are removed, suggesting room for a tighter intervention. Two directions follow naturally from the analysis: extending the trigger to feature-bias as well (the current rule only addresses the question-vs-bug imbalance), and replacing the discrete margin filter with a continuous embedding-space rebalancing that re-weights neighbors by class frequency rather than dropping them. Either direction is implementable as a drop-in replacement for our \texttt{\_debias\_neighbors} function and would preserve \bragtag's deployment-friendly properties (no training, no extra inference cost beyond the retrieval the method already performs).

\textbf{Label cleaning and richer label spaces.} The combined share of label noise (9\%), hybrid intents (13\%), and wrong template format (76\%) leaves only 3\% of residual errors as clean model failures (\Cref{sec:disc-failures}), bounding the headroom on this benchmark for any classifier within the three-class \{\textit{bug, feature, question}\} schema. Two complementary follow-ups suggest themselves. The first is template-aware preprocessing that strips or normalizes bug-template scaffolding (e.g., removing ``\textit{Type: Bug}'' auto-markers and \textit{Steps to reproduce} headers) so the classifier sees the user's actual content rather than the tooling's framing. The second is a richer label space that can express the patterns the failure analysis surfaced as recurring: a ``\textit{support-with-repro}'' label for bug-template-shaped support requests and an explicit ``\textit{hybrid}'' label for issues that legitimately combine two intents. Both directions would also benefit fine-tuning by removing systematic noise that a parametric model otherwise risks memorizing as signal.

\textbf{Generalization to other labeled-data conditions and platforms.} Our analysis covers an 11-project GitHub benchmark with a balanced 600 issues per project, which is a relatively favorable condition for retrieval. Two extensions would test the boundary of the regimes identified in \Cref{sec:disc-insights}. First, evaluating on imbalanced label distributions (the more typical case in industrial issue trackers) would test whether the retrieval-misled-error mechanism scales differently when one label dominates the index. Second, evaluating on issue trackers other than GitHub (e.g., Jira, Bugzilla) would test whether the wrong-template-format pattern generalizes; we expect platforms with stricter label vocabularies to show less of this confound but more of a different kind, such as field-misuse or sub-label drift. Both directions could reuse the methodology and replication package released here.
