\documentclass[a4paper,UKenglish,cleveref,autoref,thm-restate,anonymous]{lipics-v2021}
% NOTE: "anonymous" suppresses author block for double-blind submission.
% Remove for camera-ready after acceptance.

% ESEM 2026 Technical Track submission.
% Format: Dagstuhl LIPIcs (lipics-v2021).
% Limits: 17 pages main + up to 3 pages for Data Availability / References / Acknowledgements (mandatory: Data Availability + References).
% Submission portal: https://esem26.hotcrp.com  -- Abstract: 2026-05-11, Full paper: 2026-05-18.

\bibliographystyle{plainurl}

\usepackage{xspace}
\usepackage{booktabs}
\usepackage[most]{tcolorbox}
\usetikzlibrary{positioning,calc}


\newcommand{\votag}{VOTAG\xspace}
\newcommand{\ragtag}{RAGTAG\xspace}
\newcommand{\bragtag}{BRAGTAG\xspace}
\newcommand{\irc}{IRC\xspace}

%%% Custom bold paragraph
\makeatletter
\newcommand{\myparagraph}[1]{%
  \@startsection{paragraph}{4}{\z@}%
    {0.4\baselineskip}%
    {-1em}%
    {\sffamily\large\bfseries\raggedright}%
    *{#1}%
}
\makeatother


%%% Custom bold italic paragraph
\makeatletter
\newcommand{\myitparagraph}[1]{%
  \@startsection{paragraph}{4}{\z@}%
    {0.4\baselineskip}%
    {-1em}%
    {\sffamily\large\bfseries\itshape\raggedright}%
    *{#1}%
}
\makeatother

%%% Custom tcolorbox
\newtcolorbox{myboxi}[1][]{
  breakable,
  title=#1,
  colback=yellow!15,
  colbacktitle=white,
  coltitle=black,
  fonttitle=\bfseries,
  bottomrule=0pt,
  toprule=0pt,
  leftrule=3pt,
  rightrule=3pt,
  titlerule=0pt,
  arc=0pt,
  outer arc=0pt,
  colframe=black!60,
}

%%% Custom tcolorbox style for prompts
\begin{comment}
\definecolor{mytitlebgcolor}{HTML}{5E5E5E}
\definecolor{mybkcolor}{HTML}{f2f2ff}
\newtcolorbox{promptbox}[1]{
  colback=mybkcolor,          % body background
  colframe=black,             % black border
  coltitle=white,             % white title text
  colbacktitle=mytitlebgcolor,  % title background
  fonttitle=\small\bfseries,  % bold title
  %center title,
  title=#1,
  boxrule=0.8pt,
  arc=4pt,
  left=6pt,
  right=6pt,
  top=6pt,
  bottom=6pt
}
\end{comment}

\definecolor{mybkcolor}{HTML}{f2f2ff}
\newtcolorbox{promptbox}{
  colback=mybkcolor,  % body background
  colframe=black,     % black border
  boxrule=0.8pt,
  arc=4pt,
  left=4pt,
  right=4pt,
  top=4pt,
  bottom=4pt
}


%%%%%%%%%%%%%%%%%
\newcommand{\fixme}[1]{{\color{red}[#1]}}
\newcommand{\fixed}[1]{{\color{blue}#1}}
\newcommand{\change}[1]{{\color{orange}#1}}
\newcommand{\review}[1]{{\color{green}#1}}
\newcommand{\minor}[1]{{\color{brown}#1}}
\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\secsref}[2]{Sections~\ref{sec:#1}-\ref{sec:#2}}
\newcommand{\tabsref}[2]{Tables~\ref{table:#1}-\ref{table:#2}}
\newcommand{\figsref}[2]{Figures~\ref{fig:#1}--\ref{fig:#2}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\eqaref}[1]{Equation~\eqref{eq:#1}}
\newcommand{\lstref}[1]{Listing~\ref{lst:#1}}
\newcommand{\alref}[1]{Algorithm~\ref{al:#1}}

% --- Metadata (TODO: fill in before submission) ---
\title{Retrieval-Augmented Few-Shot Prompting vs. LoRA Fine-Tuning for Issue Report Classification: An Empirical Study}
\titlerunning{Retrieval-Augmented Few-Shot vs. Fine-Tuning for IRC} % uncomment if title is longer than one line

% An Empirical Study of Retrieval-Augmented Few-Shot Prompting for Issue Report Classification

\author{TODO: Author Name}{Affiliation, City, Country}{email@domain}{https://orcid.org/0000-0000-0000-0000}{}

\authorrunning{TODO: A. Name}
\Copyright{TODO: Author Name}

\ccsdesc[500]{Software and its engineering~Software notations and tools}
\ccsdesc[300]{Computing methodologies~Natural language processing}

\keywords{Issue classification, Retrieval-augmented generation, Fine-tuning, Large language models, Mining software repositories}

\category{}
\relatedversion{}

% \acknowledgements{TODO}

% --- Editor-only macros (do not touch) ---
\EventEditors{}
\EventNoEds{0}
\EventLongTitle{}
\EventShortTitle{}
\EventAcronym{}
\EventYear{}
\EventDate{}
\EventLocation{}
\EventLogo{}
\SeriesVolume{}
\ArticleNo{}

\begin{document}
\maketitle

\begin{abstract}
\myparagraph{Background.} Issue report classification (IRC) accelerates modern software maintenance. State-of-the-art automated IRC methods fine-tune Large Language Models (LLMs) with Low-Rank Adaptation (LoRA), which is computationally expensive and must be repeated to incorporate newly labeled issue reports or whenever the model is swapped.

\myparagraph{Aims.} We empirically investigate whether retrieval-augmented few-shot prompting offers a practical alternative to LoRA fine-tuning for IRC.

\myparagraph{Method.} Given a query issue, we retrieve its top-$k$ nearest neighbors from an index of classified issues, and propose three methods: (i) \votag, a similarity-weighted vote on the neighbors' labels, (ii) \ragtag, which presents the neighbors as classified examples in a few-shot prompt to an LLM, and (iii) \bragtag, a \ragtag\ variant with a more balanced retrieval scheme. We evaluate all three against a LoRA fine-tuning baseline on an 11-project benchmark, in both \emph{project-specific} and \emph{project-agnostic} data scope settings. Experiments use Qwen2.5-Instruct at four sizes.

\myparagraph{Results.} With project-specific data, \ragtag\ outperforms fine-tuning by 0.021--0.040 macro $F_1$ across all model sizes. Fine-tuning on cross-project data beats project-specific \ragtag\ by only 0.029 aggregate macro $F_1$ despite $11\times$ more labeled data. The balanced retrieval approach, \bragtag\, closes this performance gap, achieving statistical equivalence with fine-tuning when using a retrieval fallback for invalid LLM outputs. Averaged across model sizes, Retrieval-augmented few-shot prompting requires 33\% less peak GPU memory than fine-tuning.

\myparagraph{Conclusions.} Retrieval-augmented few-shot prompting is a practical alternative to LoRA fine-tuning for IRC, particularly when hardware resources are constrained, labeled data is limited, or the deployment has frequent model or data updates.
\end{abstract}

\input{sections/01_intro}
\input{sections/02_related}
\input{sections/03_approach}
\input{sections/04_setup}
\input{sections/05_evaluations}
\input{sections/06_discussion}
\input{sections/07_threats}
\input{sections/08_conclusion}
\input{sections/09_data_availability}

%%%%%%%%%%%%%%%%%%%% References
\clearpage
\bibliography{refs}

\end{document}
